MCC Models

### 2019-03-23 papers/full_paper/models.Rmd
ais version of model for likelihoods

```{r}
# child_ex3_pragm_model_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")

@@

>>>>

```{r}
child_ex3_pragm_model_noise<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 100, burn = 5, verbose = T)
)

%>%
   saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")

@@

```{r}
child.ex3.rsa.marginal.likelihood <-'

  var noise = uniform({a: 0, b: 1})

}

var steps = 100
var samples = 1
var mll = AIS(model, {steps:steps, samples: samples})
mll
'
```

```{r}
child_ex3_pragm_model_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)
```
